\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche

### 2012-02-24 article.tex
Removed sections and figures for black and colored belts
Added abstract

%An academic abstract typically outlines four elements germane to the completed work:

    %* The research focus (i.e. statement of the problem(s)/research issue(s) addressed);
    %* The research methods used (experimental research, case studies, questionnaires, etc.);
    %* The results/findings of the research; and
    %* The main conclusions and recommendations

  Todo.
\end{em}

@@

  \subsubsection{Colored Belt Patterns}

  % all techniques by color belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
    \caption{All techniques by color belt patterns.}
    \label{fig:patterns_color_all}
  \end{figure}

  % left techniques by color belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_left}
    %\caption{Left techniques by color belt patterns.}
    %\label{fig:patterns_color_left}
  %\end{figure}

  % right techniques by color belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_right}
    %\caption{Right techniques by color belt patterns.}
    %\label{fig:patterns_color_right}
  %\end{figure}

  \subsubsection{Black Belt Patterns}

  % all techniques by black belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
    \caption{All techniques by black belt patterns.}
    \label{fig:patterns_black_all}
  \end{figure}

  % left techniques by black belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_left}
    %\caption{Left techniques by black belt patterns.}
    %\label{fig:patterns_black_left}
  %\end{figure}

  % right techniques by black belt patterns
  %\begin{figure}
    %\includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_right}
    %\caption{Right techniques by black belt patterns.}
    %\label{fig:patterns_black_right}
  %\end{figure}

>>>>

  When performing patterns in ITF Taekwon-Do, one of the factors mentioned in
  the encyclopedia is that there should be an equal amount of techniques to
  both sides of the body. Here we analyze hand techniques in Chon-Ji through
  Juche to establish whether or not there is a bias towards either side.  This
  is done by attaching metadata, in form of tags, to each pattern movement.
  These tags are extracted from each movement's English description in the
  condensed encyclopedia, and supplemented with keywords noted while
  performing the pattern. We then apply concepts from set theory to retrieve
  information we are interested in, and find that there are seven more
  techniques on the right side than on the left.

\end{em}

@@
